% !TEX root=main.tex

Trajectory recommendation is the problem of recommending a sequence of places in a city for a tourist to visit.
It is strongly desirable for the recommended sequence to avoid loops, as tourists typically would not wish to revisit the same location.
Given some learned model that scores sequences, how can we then find the highest-scoring sequence that is loop-free?

This paper studies this problem, with three contributions.
First, we detail three distinct approaches to the problem -- 
%a heuristic inspired by Christofides' algorithm,
graph-based heuristics,
integer linear programming, and
list extensions of the Viterbi algorithm
-- and qualitatively summarise their strengths and weaknesses.
Second, we explicate how two ostensibly different approaches to the list Viterbi algorithm are in fact fundamentally identical.
Third, we conduct experiments on real-world trajectory recommendation datasets to identify the tradeoffs imposed by each of the three approaches.

Overall, our results indicate that a greedy graph-based heuristic offer excellent performance and runtime, leading us to recommend its use for removing loops at prediction time.

% Overall, we find that
% all methods offer performance improvements over na\"{i}vely predicting a sequence with loops;
% Christofides' algorithm is at least an order of magnitude faster than the other methods, but with a significant sacrifice in accuracy;
% and that the list Viterbi is faster than the ILP for short trajectories, but the ILP is superior for longer trajectories.
