% !TEX root=main.tex

We now formalise the problem of interest and outline its challenges.

%
\subsection{Trajectory recommendation}

Fix some set $\PCal$ of points-of-interest (POIs) in a city.
A \emph{trajectory}\footnote{In graph theory, this is also referred to as a walk.} is any sequence of POIs, possibly containing loops (repeated POIs).
In the \emph{trajectory recommendation} problem, we are given as input a training set of historical tourists' trajectories.
From this, we wish to design a \emph{trajectory recommender}, which accepts a
\emph{trajectory query} $\x = (s, l)$, comprising a start POI $s \in \PCal$, and trip length $l \!>\! 1$, %(\ie the desired number of POIs, including $s$),
and produces one or more sequences of $l$ POIs starting from $s$. %that conform to the query.

Formally, let $\XCal \defEq \PCal \times \{ 2, 3, \ldots \}$ be the set of possible queries,
$\YCal \defEq \bigcup_{l = 2}^\infty \PCal^l$ be the set of all possible trajectories,
and for fixed $\x \in \XCal$, $\YCal_{\x} \subset \YCal$ be the set of trajectories that conform to the constraints imposed by $\x$,
\ie if $\x = (s, l)$ then
%$\YCal_{\x} = \left\{ \y \in \PCal^l \mid y_1 = s \right\}$.
$\YCal_{\x} = \{ \y \in \PCal^l \mid y_1 = s \}$.
Then, the {trajectory recommendation} problem has:

\vspace{0.5\baselineskip}

\begin{mdframed}[innertopmargin=3pt,innerbottommargin=3pt,skipbelow=5pt,roundcorner=8pt,backgroundcolor=red!3,topline=false,rightline=false,leftline=false,bottomline=false]
	\begin{tabular}{ll}
		{\sc Input}:  & training set $\left\{ \left( \x^{(i)}, \y^{(i)} \right) \right\}_{i = 1}^n \in ( \XCal \times \YCal )^n$ \\
		{\sc Output}: & a trajectory recommender $r \colon \XCal \to \YCal$ \\
	\end{tabular}
\end{mdframed}

\vspace{0.5\baselineskip}

One way to design a trajectory recommender is to find a (query, trajectory) affinity function $f \colon \XCal \times \YCal \to \mathbb{R}$, and let
\begin{equation}
	\label{eqn:argmax}
	r( x ) \defEq \argmax_{\y \in \YCal_x}~f(\x, \y).
\end{equation}
%In particular, $\y = (s,~ y_2, \dots, y_l)$ is a trajectory with $l$ POIs. %, which has no sub-tours. %i.e. $y_j \ne y_k$ if $j \ne k$.
%This was the view proposed in~\cite{cikm16paper} where they authors considered an
%objective function that added two components together: a POI score and a transition score.
Several choices of $f$ are possible.
\citet{cikm16paper} proposed to use $f$ given by a RankSVM model. %, combined with a transition score between POIs.
While offering strong performance, this has a conceptual disadvantage highlighted in the previous section:
it does not model global cohesion, and could result in solutions such as recommending three restaurants in a row.

To overcome this, \citet{Chen:2017} proposed to use $f$ given by a structured SVM (SSVM),
wherein $f( \x, \y ) = \mathbf{w}^T \Phi( \x, \y )$ for a suitable feature mapping $\Phi$.
%In the case of an SSVM with pairwise potentials,
When this feature mapping decomposes into terms that depend only on adjacent elements in the sequence $\y$ (akin to a linear-chain conditional random field),
the optimisation in Equation \ref{eqn:argmax} can be solved with the classic Viterbi algorithm.

\input{schematic}

%
\subsection{Path recommendation}

We argue that the definition of trajectory recommendation is incomplete for a simple reason:
in most cases, a tourist will not want to revisit the same POI.
Instead, what is needed is to recommend a \emph{path}, \ie a trajectory that does not have any repeated POIs.
Let $\thickbar{\YCal} \subset \YCal$ be the set of all possible paths,
and for fixed $\x \in \XCal$, let $\thickbar{\YCal}_{\x} \subset \thickbar{\YCal}$ be the set of paths that conform to the constraints imposed by $\x$.
We now wish to construct a \emph{path recommender} $r \colon \XCal \to \thickbar{\YCal}$ via
\begin{equation}
	\label{eqn:argmax-path}
	r( x ) \defEq \argmax_{\y \in \thickbar{\YCal}_x}~f(\x, \y).
\end{equation}
For $f$ given by an SSVM, Equation \ref{eqn:argmax-path} requires we depart from the standard Viterbi algorithm, as the sequence in Equation \ref{eqn:argmax} may well have a loop.\footnote{In SSVMs, this issue also arises during training \citep{Chen:2017}, but we focus here only on the prediction problem. See \S\ref{sec:discussion} for additional comments.}
There are two distinct modes of attack available:
\begin{enumerate}
	\item seek an approximate solution to the problem,
	via heuristics that exploit a graph view of Equation \ref{eqn:argmax-path}.
	%that remove loops present in the standard Viterbi solution,
	%or by greedily constructing a loop-free solution.

	\item seek an exact solution to the problem,
	via integer linear programming,
	or top-$K$ extensions of the Viterbi algorithm. %(known as list Viterbi algorithms).
\end{enumerate}
While \citet{Chen:2017} suggested the latter exact approaches, they did not formally compare their performance either qualitatively or quantitatively;
they did not detail the different top-$K$ extensions of the Viterbi algorithm and the connections thereof;
and they did not consider approximate approaches.

In the sequel, we thus detail the above approaches in more detail.
Figure \ref{fig:schematics} gives a schematic overview of these algorithms.


% {\color{red!75}
% \begin{itemize}
%   %\item connect to workshop
%   %\item distinguish between next location vs whole trajectory
%   %\item define word usage: trajectory, path, walk, sequence, tour, etc.
%   \item describe relation to travelling salesman, and say why different
%   %\item contributions of this paper
% \end{itemize}
% }
