% !TEX root = ./main.tex

Current recommender systems largely focus on static, unstructured content.
In many scenarios, we would like to recommend content that has sequential structure,
such as %when recommending
a trajectory of points-of-interests in a city, or a playlist of songs.
% emphasize the challenge, and then sell our solution ? -- LX
\rev{Dubbed {\em Structured Recommendation}, 
this problem differs from the typical structured prediction problem 
in that there are multiple correct answers for a given input, 
and that valid predictions are sequences with no repeated elements.}
%Starting from a classic structured support vector machine,
%we propose two changes to the method %(originally designed for classification)
%enabling us to solve structured recommendation.
We propose an approach to sequence recommendation based on a variant of the classic structured support vector machine.
\rev{For prediction, we modify the inference procedure to avoid predicting loops in the sequence via the list Viterbi algorithm, an extension of the Viterbi algorithm that sequentially finds a list of top-scoring sequences. 
For training, we first modify the objective function to account for the existence of multiple ground truths for a given input. We also modify the loss-augmented inference procedure to exclude the known ground truths using the same list Viterbi algorithm.}
Experiments on real-world trajectory recommendation datasets show the benefits of our approach over existing, non-structured recommendation approaches.
